---
title: "p8105_hw1_sl5010"
output: github_document
---

```{r}
library(tidyverse)
```

## Problem 1

```{r}
df1 = tibble(
norm_sample = rnorm(10),
logical_vector= norm_sample >0,
vec_char = c("a", "b", "c", "d","e", "f", "g", "h","i","j"),
vec_factor = factor(c("cat", "dog", "bird", "cat", "dog", "bird", "cat", "dog", "bird", "bird"))
)

df1
```


```{r}
mean(pull(df1,norm_sample))
mean(pull(df1,logical_vector))
mean(pull(df1,vec_char))
mean(pull(df1,vec_factor))
```

Answer: mean of each first two variable (norm_sample, logical_vector) works, whereas the following two variable (vec_char, vec_factor) doesn't work

```{r}
as.numeric(pull(df1,logical_vector))
as.numeric(pull(df1,vec_char))
as.numeric(pull(df1,vec_factor))
```

### What happens? Why?
The logical vector become 0 and 1, true represents 1 and false represents 0. Since their values was setted as 0 and 1 in the R language base.
Character Variable become NA, that is, they are not able to be transform to numeric Variable. Since character could not be assigned values.
Factor Variable becomes 1,2 and 3. Since there are only 3 level factors.

### Does this help explain what happens when you try to take the mean?

**Yes.**Since mean can only be taken for numeric values, and the logical vector can be transfered to numeric, norm_sample was setted to be numeric. However, Character Variable and Factor Variable can not be assigned numeric values, they do not have mean.

```{r}

```

